Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-03-01 main_paper.tex
Conclusion, first take. Please check how you feel about it.

\section{Conclusion}\label{conclusion}
This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
confidence intervals in regression discontinuity designs.
The approach proposed builds upon the developments and intuition advanced by CCT and is based on a first-order bias correction.
Our procedure provides an alternative to the plug-in analytical methods in the literature and is simple to implement generating robust confidence intervals.
Simulation evidence is presented that the proposed bootstrap bias correction and confidence intervals have improved coverage and shorter length relative to the analytical alternatives proposed by CCT.

>>>>

\section{Conclusion}\label{conclusion}
This paper proposes a novel bootstrap procedure to obtain robust bias-corrected confidence intervals in regression discontinuity designs.
The approach proposed builds upon the developments and intuition advanced by CCT and is based on a first-order bias correction.
 We exploit CCT's theoretical insight through a new residual bootstrap. In particular, we propose estimating the local linear model as usual,
then estimating a local second order polynomial and generating bootstrap datasets by resampling the residuals of that polynomial.

The bootstrap sample is used to estimate the bias of the RD estimator, which is then removed from the original estimator.
 This approach is described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected estimator is shown to be asymptotically normal with mean zero in our
Theorem~\ref{T1} under AMSE-optimal bandwidth rates.

Just as in CCT, our bias correction step introduces additional variability.  So we propose then bootstrap the bias-corrected estimator itself to
 generate valid confidence intervals. This procedure, which requires bootstrapping the datasets produced by an initial bootstrap procedure, is described in Algorithm~\ref{Alg2},
 and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.

 Hence, our procedure provides an alternative to the plug-in analytical methods in the literature and is simple to implement generating robust confidence intervals.

Simulation evidence is presented that the proposed bootstrap bias correction and confidence intervals have similar empirical coverage and average interval length relative to
 the analytical alternatives proposed by CCT, making it a suitable option to practitioners.
